Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2021-12-27 paper.tex
Justify conclusion that mixing leads to slower kink growth

Our set of numerical experiments has suggested that the mixing as a result of the
nonlinear flute instability slows the growth of the kink instability.
It seems unlikely that in the linear regime the perturbations of the flute and
kink are able to directly couple, given that the kink instability generally
presents at the axis of a flux tube and the flute at some resonant surface away
from the axis. Further investigation of the nonlinear interaction between the
two instabilities is required.

>>>>

\rev{The growth rate of the kink instability is, counter-intuitively, lower in
the weakly dissipative anisotropic cases, compared to the strongly dissipative
isotropic cases, i.e. one would expect the kink instability to grow more
quickly (or at least be unaffected) when using anisotropic viscosity. Indeed,
the simulations reported in~\citet{quinnEffectAnisotropicViscosity2020} display
this behaviour, where the kink instability grows (marginally) faster in the
anisotropic cases. We conjecture it is the presence of the flute modes which
negatively affects the growth of the kink instability. It seems unlikely that
in the linear regime the perturbations of the flute and kink are able to
directly couple, given that the kink instability generally presents at the axis
of a flux tube and the flute at some resonant surface away from the axis.
Instead of a linear coupling, we believe that the linear kink instability is
affected by the more complex magnetic field configuration that arises due to
the mixing caused by the nonlinear development of the flute modes (for example,
compare figures~\ref{fig:field_line_plots_iso}
and~\ref{fig:field_line_plots_swi}).}
